Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/results.tex
add notes on version and hardware

%!TEX root = ClementiBarba2020.tex

>>>>

%!TEX root = ClementiBarba2020.tex
All the results of these paper were obtained using \pygbe (\url{https://github.com/pygbe/pygbe})
with the version at this point in the history of commits (\url{https://github.com/pygbe/pygbe/tree/e1f3650b0c99cab99dcfe5372200d3a1534eddfe}), which contains 
the Dockerfile to create the image that was used for the containers where the simulations wherr run.

All results were obtained on a lab workstation, built from parts.
Hardware specifications are as follows: 
\begin{itemize}
  \item CPU: Intel Core i7-5930K Haswell-E 6-Core 3.5GHz LGA 2011-v3
  \item RAM: G.SKILL Ripjaws 4 series 32GB (4 x 8GB)
  \item GPU: Nvidia Tesla K40c (with 12 GB memory)
\end{itemize}
